---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

##NOTE: This code is still very much in development. If you have somehow stumbled onto my GitHub to have a squizz, thanks for the interest but please advert your eyes for a moment.

# exanalysis

<!-- badges: start -->
<!-- badges: end -->

This is the accompanying package to "Reconstruction of sea-surface temperature and sea-ice concentration via exchangeability analysis".

## Installation

You can install exanalysis direct from GitHub:

``` r
devtools::install_github("astfalckl/exanalysis")
```

## Code run-through

Let us first load <tt> exanalysis </tt>

```{r example}
library(exanalysis)
## basic example code
```

The package ships with a number of rds files that contain the data used in the paper. 

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
