---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Coexchangeable process modelling for uncertainty quantification in joint climate reconstruction

<!-- badges: start -->
<!-- badges: end -->

This is the accompanying package to "Coexchangeable process modelling for uncertainty quantification in joint climate reconstruction". This <tt>.rmd</tt> file pulls some results from pre-computed results; to run the analysis from scratch look in <tt>run_analysis.R</tt>.

# Installation

To execute on your local machine you can install <tt>exanalysis</tt> direct from GitHub:

``` r
devtools::install_github("astfalckl/exanalysis")
```

and load <tt> exanalysis </tt>.

```{r warning = FALSE}
library(exanalysis)
```

```{r warning = FALSE, echo = FALSE}
library(tidyverse)
```

# Data

The package ships with a number of <tt>.rds</tt> files that contain the data used in the paper. Namely,

* <tt>model_data</tt> that contains the simulation outputs of SST,
* <tt>sst_data</tt> that contains proxy reconstructions of SST (note there are some added points to the original MARGO dataset). 
* <tt>sic_data</tt> that contains proxy reconstructions of SST (note there are some added points to the original MARGO dataset). 

These files are all lists that contain useful information to the analysis. The main contents of these lists are

## Update sea-surface temperature


```{r}
as_tibble(margo_sst$data)
```

```{r, echo = FALSE}
margo_sst$data %>%
  ggplot() +
    ggplot2::geom_point(aes(x = lon, y = lat, color = sst_obs), size = 0.5) + 
	  ggplot2::geom_polygon(
	    data = coastlines, 
	    aes(x = long, y = lat, group = group), 
	    fill = "white"
	  ) + 
	  ggplot2::geom_path(
	    data = coastlines, 
	    aes(x = long, y = lat, group = group), size = 0.3
	  ) + 
	  scico::scale_color_scico(
	  	expression(degree~"C"), direction = -1, palette = "roma"
	  ) +
	  ggplot2::scale_x_continuous(expand = c(0,0)) +
	  ggplot2::scale_y_continuous(expand = c(0,0)) +
	  ggplot2::xlab("Longitude") + 
	  ggplot2::ylab("Latitude") +
	  ggplot2::coord_fixed() +
	  ggplot2::theme_bw() +
	  ggplot2::guides(
	  	fill = ggplot2::guide_colourbar(barwidth = 0.5, barheight = 4)
	  ) +
	  ggplot2::theme(
	  	axis.text = ggplot2::element_text(size = 10), 
	  	axis.title = ggplot2::element_text(size = 10)
	  )
```
```{r, echo = FALSE}
margo_sst$data %>%
  dplyr::filter(source != "xavier") %>%
  ggplot2::ggplot() +
	  ggplot2::geom_point(aes(x = lon, y = lat, shape = source), size = 0.8) + 
	  ggplot2::geom_polygon(
	    data = coastlines, 
	    aes(x = long, y = lat, group = group), 
	    fill = "white"
	  ) + 
	  ggplot2::geom_path(
	    data = coastlines, 
	    aes(x = long, y = lat, group = group), size = 0.3
	  ) + 
		ggplot2::scale_shape_discrete("Proxy Type") +
		ggplot2::scale_x_continuous(expand = c(0,0)) +
		ggplot2::scale_y_continuous(expand = c(0,0)) +
		ggplot2::xlab("Longitude") + 
		ggplot2::ylab("Latitude") +
		ggplot2::coord_fixed() +
		ggplot2::theme_bw() +
		ggplot2::theme(
			axis.text = ggplot2::element_text(size = 10), 
			axis.title = ggplot2::element_text(size = 10)
		)
```

```{r}
as_tibble(pmip_sst$sst)
```

<!-- First thing is to generate the incidence matrices.

```{r}
H_list <- generate_H(pmip_sst, margo_sst)
utils::str(H_list)
```

Then we optimise our loss to get an estimate of the variance parameters $\alpha$ and $\kappa$. (This is being loaded from memory in the background so I don't have to wait for the fitting procedure when I'm rendering the README)

```{r, eval = FALSE}
params_hat <- train_params(sst_model, meas, H_list)
```

```{r, echo = FALSE}
params_hat <- tibble(
	tau = 6,
	alpha = 0.921,
	kappa = 1.61,
	beta = 1
)
```

```{r}
params_hat
```
 -->
## Update sea-ice concentration





















