---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Coexchangeable process modelling for uncertainty quantification in joint climate reconstruction

This is the accompanying package to "Coexchangeable process modelling for uncertainty quantification in joint climate reconstruction". This <tt>.rmd</tt> file pre-computes some results; to run the analysis from scratch look at the top section of <tt>run_analysis.R</tt>. Relatedly, <tt>run_analysis.R</tt> also contains all code to generate the paper's figures.

# Installation

To execute on your local machine you can install <tt>exanalysis</tt> direct from GitHub:

```{r eval = FALSE}
devtools::install_github("astfalckl/exanalysis")
```

and load:

```{r warning = FALSE, message = FALSE}
library(exanalysis)
library(tidyverse)
```

# Data

The package ships with a number of <tt>.rds</tt> files that contain the data used in the paper. <tt>sst_data</tt> contains the proxy reconstructions of SST (note the pseudo-observations mentioned in Section 4.2.1 are also included here). The primary data source is [the MARGO project](https://doi.pangaea.de/10.1594/PANGAEA.733406) with some data supplemented from [Benz et al. (2016)](https://www.sciencedirect.com/science/article/pii/S0277379116302062). The data structure has five components:

* <tt>data</tt> that contains the latitude, logitude, SST proxy reconstructions, reliability and sd (as listed in the MARGO project), proxy source, and an identifier of annual or summer mean value.
* <tt>coords</tt> is simply the coordinate of the SST data subsetted into a seperate tibble used for plotting.
* <tt>B</tt> and <tt>varB</tt> are the belief specifications documented in Section~5.1.
* <tt>n</tt> is the number of data points used as a global parameter in the statistical analysis.

<tt>sic_data</tt> contains the binary observed sea ice values at each of the model spatial locations. Finally, <tt>model_data</tt> contains the output of the multi-model ensemble, projected onto the FAMOUS ocean grid. The data structure has seven components:

* <tt>data</tt> that contains latitude, longitude, time instance, SST and SIC values and the MME member.
* <tt>means</tt> that contains the MME's mean SST value (i.e. $M_X$ in the paper).
* <tt>mask</tt> masks the ocean output from the global spatial grid; this is used for plotting.
* <tt>coords</tt> the model's oceanic spatial coordinates.
* <tt>n</tt>, <tt>ntime</tt> and <tt>m</tt> are global parameters of number of spatial locations, number of temporal locations and number of MME members.

These three data objects can be viewed by running
```{r, eval = FALSE}
str(sst_data, give.attr = FALSE)
str(sic_data, give.attr = FALSE)
str(model_data, give.attr = FALSE)
```

# Sea-surface temperature

To calculate the SST belief updates detailed in Section 4.2.1. we use two functions.
The first, <tt>generate_Hx()</tt>, calculates $H_x$ and the second, <tt>calculate_sst_update()</tt>, calculates the belief updates. Our prior belief specifications are stored as a tibble in <tt>sst_params_prior</tt>. To generate the SST belief updates, the code is run as

```{r, eval = FALSE}
sst_prior_params <- dplyr::tibble(tau = 6, c = 0.92, kappa = 1.61, alpha2 = 1)

h_list <- generate_Hx(model_data, sst_data)

sst_update <- calculate_sst_update(
  model_data, sst_data, h_list, sst_prior_params
)
```

<tt>h_list</tt> is a list data structure that composes of the spatial, temporal, and spatio-temporal components of $H_x$. In the back of the <tt>calculate_sst_update()</tt> code we use the different components of $H_x$ to enable some algebraic tricks to speed computation. The main results of the analysis are calculated by <tt>calculate_sst_update()</tt> and stored, here, in <tt>sst_update</tt>. The list <tt>sst_update</tt> stores most of the information that has gone into the calculation as well as the output. The first level items are

* <tt>simulation</tt>, the model data.
* <tt>proxy</tt>, the reconstructed proxy data.
* <tt>E</tt>, <tt>Vs</tt> and <tt>Vt</tt>, the adjusted expectation and variances (decomposed into spatial and temporal components) stored as matrix objects for future calculations.
* <tt>update_tbl</tt> is the main results of the analysis and is a tibble that stores first and second adjusted expectations and marginal variances linked to the spatio-temporal locations. This tibble is used to plot Figure 3.

# Update sea-ice concentration

Calculating SIC belief updates require a bit more involvement than the SST updates. First, we set the spline basis functions in the <tt>spline_params</tt> objects and specify the prior specfications in <tt>sic_prior_params</tt>. As we model SIC as a function of SST, we also require a spatio-temporal SST field; as detailed in the main body of the paper, here we use simply use the adjusted expectation, and call this quantity <tt>sst_field</tt>. The projection $\hat{\beta}_i$ are calculated from <tt>project_betais()</tt> and finally, the main updates of SIC beliefs are calculated in <tt>calculate_sic_update()</tt>.

```{r, eval = FALSE}
spline_params <- list(
  bounds = c(-1.92, 10),
  knots = c(-1.15, -0.32, 1.44),
  degree = 1,
  prior_exp = c(0.16, 0.47, 0.27, 0.1, 0)
)

sic_prior_params <- list(
  corW_params = c(6, 4, 1, 0),
  varU_params = c(6, 4, 0.3, 0)
)

sst_field <- as.numeric(sst_update$update_tbl$Eadj2)

betais <- project_betais(sst_update, spline_params)

sic_update <- calculate_sic_update(
  sst_update, spline_params, sic_prior_params, betais, sst_field, sic_data
)
```

The output <tt>sic_update</tt> contains

* <tt>data</tt>, the SIC binary data.
* <tt>adj_exp_spline_tbl</tt> and <tt>adj_exp_spline_tbl</tt> the adjusted expectations and variances of the spline coefficients. These are used to generate the individual spline fits in Figure 4.
* <tt>E</tt>, <tt>V</tt> and <tt>V_param_update</tt>, the adjusted expectation and variances (of the parameter coeffecients and of the spatio-temporal SIC values) stored as matrix objects.
* <tt>update_tbl</tt> is, again, the main results of the analysis. Similarly to SST, this tibble stores first and second adjusted expectations and marginal variances of SIC linked to the spatio-temporal locations. This tibble is used to plot Figure 5.
