---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

##NOTE: This code is still very much in development. If you have somehow stumbled onto my GitHub to have a squizz, thanks for the interest but please advert your eyes for a moment.

# exanalysis

<!-- badges: start -->
<!-- badges: end -->

This is the accompanying package to "Reconstruction of sea-surface temperature and sea-ice concentration via exchangeability analysis".

## Installation

You can install <tt> exanalysis </tt> direct from GitHub:

``` r
devtools::install_github("astfalckl/exanalysis")
```

## Code run-through

Let us first load <tt> exanalysis </tt> and some other dependencies.

```{r example}
	library(exanalysis)
	library(tidyverse)
```

The package ships with a number of rds files that contain the data used in the paper. Namely, there is

	* <tt> pmip_sst </tt> that contains the simulation outputs of SST,
	* <tt> margo_sst </tt> that contains proxy reconstructions of SST (note there are some added points to the original MARGO dataset). 

These files are all lists that contain useful information to the analysis. The main contents of these lists are

```{r}
	as_tibble(pmip_sst$sst)
```

```{r}
	as_tibble(margo_sst$data)
```

First thing is to generate the incidence matrices.

```{r}
	H_list <- generate_H(pmip_sst, margo_sst)
	utils::str(H_list)
```

Then we optimise our loss to get an estimate of the variance parameters $\alpha$ and $\kappa$. (This is being loaded from memory in the background so I don't have to wait for the fitting proceedure when I'm rendering the README)

```{r, eval = FALSE}
	params_hat <- train_params(sst_model, meas, H_list)
```

```{r, echo = FALSE}
	params_hat <- tibble(
		tau = 6,
		alpha = 0.921,
		kappa = 1.61,
		beta = 1
	)
```

```{r}
params_hat
```



















