---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

##NOTE: This code is still very much in development. If you have somehow stumbled onto my GitHub to have a squizz, thanks for the interest but please advert your eyes for a moment.

# exanalysis

<!-- badges: start -->
<!-- badges: end -->

This is the accompanying package to "Reconstruction of sea-surface temperature and sea-ice concentration via exchangeability analysis".

## Installation

You can install <tt> exanalysis </tt> direct from GitHub:

``` r
devtools::install_github("astfalckl/exanalysis")
```

## Code run-through

Let us first load <tt> exanalysis </tt>

```{r example}
library(exanalysis)
```

The package ships with a number of rds files that contain the data used in the paper. Namely, there is
	* <tt> pmip_sst </tt> that contains the simulation outputs of SST,
	* <tt> margo_sst </tt> that contains proxy reconstructions of SST (note there are some added points to the original MARGO dataset).

```{r}
pmip_sst
```

```{r}
margo_sst
```

